---
title: "OEE For 3D Printers"
author: "Andrew Rosa"
date: "5/27/2017"
output:
        html_document:
                includes:
                        in_header: head.html
                css: style.css
---



```{r warning=FALSE}
library(knitr)
printer_1 <- read.csv(file = "~/Desktop/Oee_for_3D_Printers/Printer1Data.csv")
kable(printer_1, caption = "Printer 1 Data-Set")
```

###Availibility

Machine time is the total elasped_time in min.

```{r}
machine_time <- sum(printer_1$elapsed_time)
```

availibility is the machine time divided by the shift time in min (this is a 11.5 hour shift)

```{r}
shift <- 11.5 * 60
availibility <- machine_time / shift
```

###Quality

quality is the number of good parts divided by the total number of parts

```{r}
total_parts <- sum(printer_1$parts)
good_parts <- sum(printer_1$successful_parts)
quality <- good_parts / total_parts
```

###Performance

For the theoritical output you need to find the average time is takes to print a part part per min is calculated by dividing the number of parts on a plate with the estimated print time average parts per minute is the mean of all the part per minute for slices ran on the bot for a givien day

```{r}
printer_1$parts_per_min <- printer_1$parts / printer_1$est_time
ave_parts_per_min <- mean(printer_1$parts_per_min)
```

Theoritical outpout is the product of the machine time and average parts per min

```{r}
theo_output <- machine_time * ave_parts_per_min
```

performance is the total number of parts produced divided by the theoritical output

```{r}
performance <- total_parts / theo_output
```

###OEE

Finally OEE is the product of availability quality and performance. 

```{r}
oee <- availibility * quality * performance
```











